Meta-analysis

### 2020-08-31 04_MetaAnalysis.Rmd
Updated objects to remove run errors

   - We will test spray management (our treatment) as a fixed effect and random interactive term to trial

```{r metafor_organisation}
dat1 <-
   PM_MB_dat %>%
   mutate(vi = vi/n) %>% 
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "control",
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          D_pres = 
             factor(D_pres,
                    c("lowD",
                      "highD")),
          id = row_number()) %>%
   dplyr::select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      yield_gain,
      dose,
      vi,
      yield_error,
      vi2,
      n,
      id)
```

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~1 | id), 
   struct = "UN",
   control=list(optimizer="optim"),
   data = dat1
)

@@

Does disease pressure on the crop affect the optimum spray scenario? 
Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(PM_MB_dat[PM_MB_dat$spray_management == "Late"| PM_MB_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r max(as.numeric(PM_MB_dat[PM_MB_dat$spray_management == "Late"|                   PM_MB_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
Lets test this hypothesis by adding it as a moderator and comparing the new model with the original model above.

```{r DisPressComparison}
PM_mv2 <- rma.mv(
   yi = grain_yield.t.ha,
   vi,
   mods = ~ spray_management*D_pres,
   method = "ML",
   random = list(~ spray_management | trial, ~1 | id), 
   struct = "UN",
   control=list(optimizer="optim"),
   data = dat1
)

anova(PM_mv, PM_mv2)
```
We can see that the lower $QE$ indicates that disease pressure moderator helped explain some of the residual heterogeneity in differences in grain yield between treatments. 
However according to the Wald-test the models were not significantly different and we should use the original "Reduced" model.

The P value was close to the 0.05 cut-off so we will present the model output for the interest of the readers.
```{r DissPressMetMod}
summary(PM_mv2)
summary(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey"))), test=adjusted("none"))
# plot(glht(PM_mv2, linfct=cbind(contrMat(rep(7,12), type="Tukey")))) # I think this plot is too busy to be incorporated
```

@@

### Forest plot of trial treatment effect per trial
Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 40, fig.width=17}
# THIS NEEDS TO BE FIXED
source(here("R/change_labels.R"))
source(here("R/forest_rows.R"))

### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
index1 <- dat1 %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management = 
             factor(spray_management, 
                    levels = c("Early","Late","Recommended",
                    "Recommended_plus","Late_plus"))) %>%
   arrange(desc(spray_management), location, desc(grain_yield.t.ha)) %>%
   mutate(ID2 = order(ID))%>%
   pull(ID2)

### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
### this list can be used below to reference where to plot each variable
rows1 <- forest_rows(head_row = 186, 
                     ord_var = dat1$spray_management, 
                     index = index1, 
                     gap = 5, 
                     row_offset = -2)

@@

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = rows1$trows-1.5,
                ilab = cbind(dat1$year, 
                             dat1$row_spacing, dat1$host_genotype, dat1$dose),
                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
                slab = NA, 
                xlim = c(-2, 4),
                ylim = c(5,190),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.2,0.15,0.2),
                at = seq(-0.5,3, 0.5))

@@

```{r netmeta-analysis}
datPM3 <- PM_MB_dat %>%
   group_by(trial, spray_management, n) %>%
   summarize(yi_mean = mean(grain_yield.t.ha),
             vi_mean = mean(yield_error)) %>%
   ungroup()

@@

```{r Save_meta_data, eval=FALSE}
save(dat1, efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
     file = here("cache/Meta-analysisData.Rdata"))
```

>>>>

   - We will test spray management (our treatment)

@@

```{r Metafor-analysis}
PM_mv <- rma.mv(
   yi = grain_yield.t.ha.,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list(~ spray_management | trial, ~1 | id), 
   struct = "UN",
   control=list(optimizer="optim"),
   data = PM_MB_dat
)

@@

@@

### Forest plot of trial treatment effect per trial
Lets look at the trial variability in this model with a forest plot
```{r forestP, eval=FALSE, fig.height=40, fig.width=17, include=FALSE}
# THIS NEEDS TO BE FIXED
source(here("R/change_labels.R"))
source(here("R/forest_rows.R"))

### Sort and arrange data-frame accordingly and produce a index vector to inform the order of each "Trial" on the plot
index1 <- PM_MB_dat %>%
   mutate(ID = seq_along(trial_ref)) %>%
   mutate(spray_management = 
             factor(spray_management, 
                    levels = c("Early","Late","Recommended",
                    "Recommended_plus","Late_plus"))) %>%
   arrange(desc(spray_management), location, desc(grain_yield.t.ha.)) %>%
   mutate(ID2 = order(ID))%>%
   pull(ID2)

### Use forest rows function to return a list of where to place on the plot: sub-titles, each trial row, and summary prediction for each treatment.
### this list can be used below to reference where to plot each variable
rows1 <- forest_rows(head_row = 186, 
                     ord_var = PM_MB_dat$spray_management, 
                     index = index1, 
                     gap = 5, 
                     row_offset = -2)

@@

forest1  <- metafor::forest(PM_mv, cex = 1.15 , width = 5,
                #order = "fit",
                rows = rows1$trows-1.5,
                ilab = cbind(PM_MB_dat$year, 
                             PM_MB_dat$row_spacing, PM_MB_dat$host_genotype, PM_MB_dat$dose),
                ilab.xpos = c(-2.35,-2.1,-1.8,-1.4)+1,
                slab = NA, 
                xlim = c(-2, 4),
                ylim = c(5,190),
                xlab = "Grain yield mean difference",
                addfit = FALSE,
                efac = c(0.2,0.15,0.2),
                at = seq(-0.5,3, 0.5))

@@

```{r netmeta-analysis}
datPM3 <- PM_MB_dat %>%
   group_by(trial, spray_management, n) %>%
   summarize(yi_mean = mean(grain_yield.t.ha.),
             vi_mean = mean(vi)) %>%
   ungroup()

@@

```{r Save_meta_data, eval=FALSE}
save(efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
     file = here("cache/Meta-analysisData.Rdata"))
```
